\section{Future Work}
\label{sec:futurework}
Future work includes both adding features and improving performance.

Currently, our system allows any user to see any other user's session 
and listen to any music session. Ideally, users would be able to control 
who can see and listen to their sessions by creating 
access control lists (ACLs). Then, a user would only see 
the sessions to which they have access. While we have `add' and `remove' 
buttons that allow users to create ACLs, currently our system does not 
use this information to control sessions. The next step would be to 
use these ACL to actually control access. A nice feature to go along with this 
would be to allow users to `search' for other users. The add and remove 
buttons only allow exact match of other user's email addresses. Another nice feature, 
like that in Google Hangouts \cite{googlehangouts}, would be to allow users to 
invite other users to join a session by e-mail. 

In terms of performance and scalability, the easiest improvement we could make would be 
to use memcache in combination with the data stores. This could improve 
the response time for a client to join a session, since joining a session 
involves a lookup in a datastore for session and listener information. 
Another improvement we could make is to make incremental updates. For example,
when a listener is removed from the listener list, instead of sending the entire 
list minus that listener, we could just send the listener that is being removed and let 
each client remove it. 

