\section{Implementation}
\label{sec:implementation}
Our client is written in JavaScript and uses SoundManager, a
JavaScript audio player API \cite{soundmanager}. In contrast, our server code is
written in Python 2.7. Both use the Google App Engine API \cite{appengine}. In
Section~\ref{sec:channel}, Section~\ref{sec:storage} and Section~\ref{sec:considerations} 
we discuss how we utilize Google App Engine in our implementation.

\subsection{Client and Server Communication}
\label{sec:channel}
When the client wants to contact the server, it issues an HTTP
request, which is handled by the appropriate Python script handler.
Handlers in Google App Engine can only serve requests within a
time limit, which is why we chose to store session data within
the Datastore.

In contrast, when the server wants to contact a client, is uses 
the Channel service. Channels are persistent connections that 
allow updates to propagate to clients without the use of polling.
This is the mechanism with which we send updates to participants
of a session. A channel is created as follows: 
\begin{enumerate}
  \item The client contacts the server
  \item The server generates a channel ID and sends back a token
  \item The client connects to the channel using the token
\end{enumerate}
The client receives updates by listening on the channel by opening
a socket and does appropriate actions based on the message received.
Updates to the channel are made via HTTP requests from clients. When
a client disconnects from the channel, a message containing the 
corresponding channel ID is sent to the server, and appropriate
cleanup is performed.

\subsection{Datastore and Blobstore}
\label{sec:storage}
As mentioned before, Datastore and Blobstore are used to store a 
variety of information. Both Datastore and Blobstore have constant access time and are highly 
reliable means of storage. Google App Engine's Datastore uses the
High Replication Datastore built atop BigTable \cite{bigtable}. Writes
use the Paxos algorithm and changes are propagated to non-participating
replicas asynchronously. App Engine Datastore 
provides high read/write availability, atomic transactions, and
strong read consistency using get(). Queries, however, only 
guarantee eventual consistency. Thus, for our application, we use
get() to retrieve entries for time-sensitive operations, such as 
propagating control commands from the host, and queries for less 
urgent actions. \cite{appengine}\cite{datastore}

Blobstore is a datastore that holds large data objects (blobs) that 
are too big to be stored in the Datastore. Once a blob has been 
created, it cannot be modified; thus, it can be considered read-only
storage. We choose Blobstore to serve our content due to the higher
file size limit. Moreover, it also performs automatic caching on its 
data. \cite{appengine}

\section{Design Considerations}
\label{sec:considerations}
We made certain decisions in order to achieve the goals discussed
in Section~\ref{sec:intro}. In this section we summarize and discuss these choices.
\begin{enumerate}
  \item \textbf{Performance}: Songs are fetched by the client as soon as they are available, 
  		allowing for seamless transitions between songs.
  		We also perform synchronization, as discussed in Section~\ref{sec:sync}, 
  		and use eventually consistent queries when possible, as mentioned in 
  		Section~\ref{sec:storage}.
  \item \textbf{Availability}: We rely on Google services such as 
  		Datastore and Blobstore, which are highly replicated and reliable. 
  		In addition, HTTP requests to the server are served as long as 
  		Google App Engine is available. We discuss how our system
		behaves with various failure modes in Section~\ref{sec:faultTolerance}.
  \item \textbf{Scalability}: For scalability purposes, we allow concurrent requests.
  		To minimize the number and size of messages, we allow incremental
  		updates. We do not send all session data on an update except when
  		a listener joins a session.
\end{enumerate}

\subsection{Fault Tolerance}
\label{sec:faultTolerance}
There are several components of our system that could fail. The host or listener
of a session could lose connection to the server or the master/session server
could go down. We discuss each type of
failure below with respect to the impact on other users of the system.

When the host of a session goes down, the system mainly continues
to operate as normal. Any listeners in the session of the down host
will continue playing the current song until completion. At that
time, they will wait until the host reconnects and updates the
session server with new information. Other clients will still be
able to join the session, but will have to wait like the current
listeners. Once the host reconnects, it rejoins its hosted session
and continues playback as if it just joined the session.

A listener losing connection has very little impact on the system. The session
server will detect the channel failure and cleanup necessary state
associated with the listener. Other listeners as well as the host
of the session will not be impacted by the disconnected listener.

When the master handler fails, active sessions continue to
operate as before. Hosts and listeners can continue to listen
together to existing and newly added songs. However, new clients
attempting to connect to the system will have their requests time
out because the master handler manages all initial client connections.

If the session handler fails, all session updates will fail.
Clients will finish the current song of their session and then
will have to wait for the session handler to come back up. New clients
first connecting to the system will be able to login, but will not
be able to join a session. They will also be unable to start a session until
the session handler comes back up.

Note, however, that Google App Engine uses multiple web servers to
handle requests reliably and that requests can be handled by any of
those servers. Moreover, the number of servers is automatically 
adjusted based on load. Thus, as long as there is at least one server available
running our handlers the system will operate as normal.